---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ACEsimFit

<!-- badges: start -->

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![R package version](https://www.r-pkg.org/badges/version/ACEsimFit)](https://cran.r-project.org/package=discord)
[![Package downloads](https://cranlogs.r-pkg.org/badges/grand-total/ACEsimFit)](https://cran.r-project.org/package=ACEsimFit)</br>
[![R-CMD-check](https://github.com/R-Computing-Lab/ACEsimFit/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/R-Computing-Lab/ACEsimFit/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/R-Computing-Lab/ACEsimFit/graph/badge.svg)](https://app.codecov.io/gh/R-Computing-Lab/ACEsimFit)
![License](https://img.shields.io/badge/License-GPL_v3-blue.svg)

<!-- badges: end -->

The goal of ACEsimFit is 1) to simulate kin pairs data based on the theory of ACE models. 2) to fit data with ACE models

## Installation

You can install the official version of ACEsimFit like so:
``` r
install.packages("ACEsimFit")
```

You can also install/update ACEsimFit with the development version of ACEsimFit from [GitHub](https://github.com/) with:

``` r
# If devtools is not installed, uncomment the line below.
# install.packages('ACEsimFit')
devtools::install_github('R-Computing-Lab/ACEsimFit')
```
## Citation

If you use `ACEsimFit` in your research or wish to refer to it, please cite the following paper:

```{r eval=TRUE, comment=NA}
citation(package = "ACEsimFit")
```
## Example

For user guide and procudure, please check out the examples in the vignette.
