---
title: "Simulation"
author: "Cailey Fay & Mason Garrison"
date: "2026-05-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(OpenMx)
library(tidyr)
library(ggplot2)
library(dplyr)
library(ACEsimFit)
library(polycor)
library(purrr)
source("~/Documents/Research/Github/risky_gambling/ACEsimFit2/R/Sim_Fit2.R")
source("~/Documents/Research/Github/risky_gambling/ACEsimFit2/R/kinsim_double2.R")
source("~/Documents/Research/Github/risky_gambling/ACEsimFit2/R/fit_OrdACE.R")
source("~/Documents/Research/Github/risky_gambling/ACEsimFit2/R/Harvest.R")
source("~/Documents/Research/Github/risky_gambling/data/miFunctions.R")
source("~/Documents/Research/Github/risky_gambling/ACEsimFit2/R/Internal.R")
```


Example: generating three sets identical except they are 25%, 50%, and 75% censored (with sibs and half sibs)
```{r}
source("~/Documents/Research/Github/risky_gambling/ACEsimFit2/R/plotSim.R")
results_fit1 <- Sim_Fit2(
  GroupNames = c("FS", "HS"),
  GroupSizes = c(1000, 1000),
  nIter = 20,
  SSeed = 62,
  GroupRel = c(.5, .25), 
  GroupR_c = c(1, 1),
  nth = 4,
  mu = c(0,0), 
  ace1 = c(.6, .2, .2), 
  ace2 = c(.6, .2, .2),
  prop_missing = c(.2,.2),
  ifComb = FALSE,
  lbound = FALSE,
  saveRaw = FALSE,
  Ord = TRUE)

use_for_plots1 <- make_parameter_df(results_fit = results_fit1, GroupRel = c(.5, 0.25), prop_missing = c(.2,.2), true_A = .6, true_C = .2, true_E = .2)

results_fit2 <- Sim_Fit2(
  GroupNames = c("FS", "HS"),
  GroupSizes = c(1000, 1000),
  nIter = 20,
  SSeed = 63,
  GroupRel = c(.5, .25), 
  GroupR_c = c(1, 1),
  nth = 4,
  mu = c(0,0), 
  ace1 = c(.6, .2, .2), 
  ace2 = c(.6, .2, .2),
  prop_missing = c(.50,.50),
  ifComb = FALSE,
  lbound = FALSE,
  saveRaw = FALSE,
  Ord = TRUE)

use_for_plots2 <- make_parameter_df(results_fit = results_fit2, GroupRel = c(.5, 0.25), prop_missing = c(.50,.50), true_A = .6, true_C = .2, true_E = .2)

 results_fit3 <- Sim_Fit2(
   GroupNames = c("FS", "HS"),
   GroupSizes = c(1000, 1000),
   nIter = 20,
   SSeed = 64,
   GroupRel = c(.5, .25),
   GroupR_c = c(1, 1),
   nth = 4,
   mu = c(0,0),
   ace1 = c(.6, .2, .2),
   ace2 = c(.6, .2, .2),
   prop_missing = c(.70,.70),
   ifComb = FALSE,
   lbound = FALSE,
   saveRaw = FALSE,
   Ord = TRUE)

use_for_plots3 <- make_parameter_df(results_fit = results_fit3, GroupRel = c(.5, 0.25), prop_missing = c(.70,.70), true_A = .6, true_C = .2, true_E = .2)

results_fit4 <- Sim_Fit2(
  GroupNames = c("FS", "HS"),
  GroupSizes = c(1000, 1000),
  nIter = 20,
  SSeed = 64,
  GroupRel = c(.5, .25), 
  GroupR_c = c(1, 1),
  nth = 4,
  mu = c(0,0), 
  ace1 = c(.6, .2, .2), 
  ace2 = c(.6, .2, .2),
  prop_missing = c(.1,.1),
  ifComb = FALSE,
  lbound = FALSE,
  saveRaw = FALSE,
  Ord = TRUE)

use_for_plots4 <- make_parameter_df(results_fit = results_fit4, GroupRel = c(.5, 0.25), prop_missing = c(.1,.1), true_A = .6, true_C = .2, true_E = .2)

results_fit5 <- Sim_Fit2(
  GroupNames = c("FS", "HS"),
  GroupSizes = c(1000, 1000),
  nIter = 20,
  SSeed = 64,
  GroupRel = c(.5, .25),
  GroupR_c = c(1, 1),
  nth = 4,
  mu = c(0,0),
  ace1 = c(.6, .2, .2),
  ace2 = c(.6, .2, .2),
  prop_missing = c(0.05,0.05),
  ifComb = FALSE,
  lbound = FALSE,
  saveRaw = FALSE,
  Ord = TRUE)

use_for_plots5 <- make_parameter_df(results_fit = results_fit5, GroupRel = c(.5, 0.25), prop_missing = c(0,0), true_A = .6, true_C = .2, true_E = .2)

results_fit6 <- Sim_Fit2(
  GroupNames = c("FS", "HS"),
  GroupSizes = c(1000, 1000),
  nIter = 20,
  SSeed = 64,
  GroupRel = c(.5, .25), 
  GroupR_c = c(1, 1),
  nth = 4,
  mu = c(0,0), 
  ace1 = c(.6, .2, .2), 
  ace2 = c(.6, .2, .2),
  prop_missing = c(.3,.3),
  ifComb = FALSE,
  lbound = FALSE,
  saveRaw = FALSE,
  Ord = TRUE)

use_for_plots6 <- make_parameter_df(results_fit = results_fit6, GroupRel = c(.5, 0.25), prop_missing = c(.30,.30), true_A = .6, true_C = .2, true_E = .2)

results_fit7 <- Sim_Fit2(
  GroupNames = c("FS", "HS"),
  GroupSizes = c(1000, 1000),
  nIter = 20,
  SSeed = 64,
  GroupRel = c(.5, .25), 
  GroupR_c = c(1, 1),
  nth = 4,
  mu = c(0,0), 
  ace1 = c(.6, .2, .2), 
  ace2 = c(.6, .2, .2),
  prop_missing = c(.40,.40),
  ifComb = FALSE,
  lbound = FALSE,
  saveRaw = FALSE,
  Ord = TRUE)

use_for_plots7 <- make_parameter_df(results_fit = results_fit7, GroupRel = c(.5, 0.25), prop_missing = c(.40,.40), true_A = .6, true_C = .2, true_E = .2)

results_fit8 <- Sim_Fit2(
  GroupNames = c("FS", "HS"),
  GroupSizes = c(1000, 1000),
  nIter = 20,
  SSeed = 64,
  GroupRel = c(.5, .25), 
  GroupR_c = c(1, 1),
  nth = 4,
  mu = c(0,0), 
  ace1 = c(.6, .2, .2), 
  ace2 = c(.6, .2, .2),
  prop_missing = c(.60,.60),
  ifComb = FALSE,
  lbound = FALSE,
  saveRaw = FALSE,
  Ord = TRUE)

use_for_plots8 <- make_parameter_df(results_fit = results_fit8, GroupRel = c(.5, 0.25), prop_missing = c(.60,.60), true_A = .6, true_C = .2, true_E = .2)


#make one frame 
plot_time <- rbind(use_for_plots1, use_for_plots2, use_for_plots3, 
                   use_for_plots4, use_for_plots5, 
                   use_for_plots6, use_for_plots7, use_for_plots8)
```

plots - at some point I might make a function to handle this because its pretty formulaic 
this gives bias for A,C,E and then the density distributions - which can be faceted by analysis, level of missingness, or just filtered down to one set of interesting results 

```{r}

#one time plot of this (practice before needing to repeat a bunch)
#I want a line for each analysis, I want x to be the prop_missingness, and I want y to be the bias, and I want three graphs - A, C, E 

ggplot(plot_time, mapping = aes(x = censored1, y = Bias_A, fill = Analysis, color = Analysis)) +
     scale_color_manual(values = c("Ordinal" = "#9E7E38","Interval" = "#4A4E41")) + 
     scale_fill_manual(values = c("#9E7E38","#4A4E41")) +
     geom_smooth() +
     scale_y_continuous(limits = c(-.3, .3)) +
     geom_ribbon(aes(ymin = mean_bias_A - 1.96 * se_bias_A, 
                  ymax = mean_bias_A + 1.96 * se_bias_A), 
              alpha = 0.1, color = NA) +
     theme_minimal() + 
     labs( title = "Estimation Bias of A",
           x = "Proportion of Censored Cases",
           y = "Deviation from Simulated Parameter")

#C

ggplot(plot_time, mapping = aes(x = censored1, y = Bias_C, fill = Analysis, color = Analysis)) +
     scale_color_manual(values = c("Ordinal" = "#9E7E38","Interval" = "#4A4E41")) + 
     scale_fill_manual(values = c("#9E7E38","#4A4E41")) +
     geom_smooth() +
     scale_y_continuous(limits = c(-.3, .3)) +
     geom_ribbon(aes(ymin = mean_bias_A - 1.96 * se_bias_A, 
                  ymax = mean_bias_A + 1.96 * se_bias_A), 
              alpha = 0.1, color = NA) +
     theme_minimal() + 
     labs( title = "Estimation Bias of C",
           x = "Proportion of Censored Cases",
           y = "Deviation from Simulated Parameter")

#E

ggplot(plot_time, mapping = aes(x = censored1, y = Bias_E, fill = Analysis, color = Analysis)) +
     scale_color_manual(values = c("Ordinal" = "#9E7E38","Interval" = "#4A4E41")) + 
     scale_fill_manual(values = c("#9E7E38","#4A4E41")) +
     geom_smooth() +
     scale_y_continuous(limits = c(-.3, .3)) +
     geom_ribbon(aes(ymin = mean_bias_A - 1.96 * se_bias_A, 
                  ymax = mean_bias_A + 1.96 * se_bias_A), 
              alpha = 0.1, color = NA) +
     theme_minimal() + 
     labs( title = "Estimation Bias of E",
           x = "Proportion of Censored Cases",
           y = "Deviation from Simulated Parameter")

#for density distributions
#can in theory use plot time here but you need to filter for a specific censorship level first or it will be wonky

#plot <- 
ggplot(plot_time) +
  geom_density(aes(x = A, fill = "Additive Genetic (A)"), alpha = 0.4, color = "#9E7E38") +
  geom_density(aes(x = C, fill = "Shared Environment (C)"), alpha = 0.4, color = "#D4AF37") +
  geom_density(aes(x = E, fill = "Error (E)"), alpha = 0.4, color = "#4A4E41") +
  
  geom_vline(xintercept = true_A, color = "#9E7E38", linetype = "dashed", size = 1) +
  geom_vline(xintercept = true_C, color = "#D4AF37", linetype = "dashed", size = 1) +
  geom_vline(xintercept = true_E, color = "#4A4E41", linetype = "dashed", size = 1) +
  scale_fill_manual(
  values = c(
    "Additive Genetic (A)" = "#9E7E38",
    "Shared Environment (C)" = "#D4AF37",
    "Error (E)" = "#4A4E41")) +

  facet_wrap(censored1~Analysis) +
     
     
     scale_x_continuous(limits = c(0, 1)) +

    theme_minimal() +
  
  theme(axis.title.x = element_blank(),
    text = element_text(family = "Baskerville", color = "black"),#not to self turn the text to white and then its ready for poster (already has transparent background)
    panel.background = element_rect(fill = "transparent", color = NA),
    plot.background = element_rect(fill = "transparent", color = NA),
    panel.grid = element_blank(),
    axis.ticks.y = element_blank(),
    legend.position = c(0.8, 0.4)) +

    labs(title = "Distribution of Simulation Results",
       subtitle = "Siblings and Half Siblings",
       y = "Density",
       fill = "Parameter Estimate")

#ggsave('simresults.PNG', plot, bg = 'transparent', dpi = 300)
     
```

I'm also interested in varying the ratio of sibs to half sibs and seeing what that does - will need to follow up with power analyses because it is probably more of a power thing than an analysis type (ordinal might suck with more disproportionate ratio just because of cell size issues)

```{r}










```
